Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-10-27 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{figure*}
        \centering\includegraphics{figures/comparison-scenarios.pdf}
        \caption{Illustration of the expected counts for the different source scenarios we used to make test datasets. The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}). For the instrument scenario \chandra we convolved the with a narrow Gaussian shaped PSF of width $\sigma=2$~pix. For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix and a five times increased effective are. All images are of size $128{\times}128$ pixels. \vlk{Please avoid using "A.U." for anything but Astronomical Units!}
        }
        \label{fig:scenarios}
        \script{comparison-scenarios.py}
    \end{figure*}

>>>>

    \begin{figure*}
        \centering\includegraphics{figures/scenarios.pdf}
        \caption{Illustration of the expected counts for the different source scenarios we used to make test datasets. The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}). For the instrument scenario \chandra we convolved the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix. For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix and a five times increased effective are. All images are of size $128{\times}128$ pixels.
        }
        \label{fig:scenarios}
        \script{scenarios.py}
    \end{figure*}
